PCA

### 2019-12-31 analysis/02_PCA.Rmd
new tsne

chartsne <- subsetmaketsne(tissuelevels, charlevels, sexlevels)
hyptsne <- subsetmaketsne("hypothalamus", charlevels, sexlevels)
pittsne <- subsetmaketsne("pituitary", charlevels, sexlevels)
gontsne <- subsetmaketsne("gonads", charlevels, sexlevels)

@@

@@

@@

def <- plot_grid(d,e, f, nrow =  1,  labels = c("d", "e", "f"), label_size = 12)
def
```

@@

@@

gh <- plot_grid(g,h, legend, nrow = 1, rel_widths = c(1, 1, 1), labels = c("h", "i", NULL ), label_size = 12)
gh
plot_grid(def, gh, nrow = 2)
```

```{r PCA-tSNE, fig.height= 7, fig.width=7}
plot_grid( abc, def, gh, nrow = 3)

>>>>

chartsne <- subsetmaketsne(tissuelevels, charlevels, sexlevels)
hyptsne <- subsetmaketsne("hypothalamus", charlevels, sexlevels)
pittsne <- subsetmaketsne("pituitary", charlevels, sexlevels)
gontsne <- subsetmaketsne("gonads", charlevels, sexlevels)
alltsne <- subsetmaketsne(tissuelevels, alllevels, sexlevels)

@@

a2 <- plotcolorfultsnes(alltsne, alltsne$tissue, colorstissue)  
b2 <- plotcolorfultsnes(alltsne, alltsne$sex, sexcolors)   
c2 <- plotcolorfultsnes(alltsne, alltsne$treatment, colorscharmaip)

abc2 <- plot_grid(a2,b2,c2, nrow = 1, labels = c("a", "b", "c"), label_size = 12)
abc2

@@

allpca <- subsetmakepca(tissuelevels, alllevels, sexlevels)
```

@@

def <- plot_grid(d,e, f, nrow =  1,  labels = c("d", "e", "f"), label_size = 12)
def

d2 <- plotcolorfulpcs(allpca, allpca$tissue, colorstissue)  
e2 <- plotcolorfulpcs(allpca, allpca$sex, sexcolors) 
f2 <- plotcolorfulpcs(allpca,allpca$treatment, colorscharmaip)

def2 <- plot_grid(d2,e2, f2, nrow =  1,  labels = c("d", "e", "f"), label_size = 12)
def2
```

@@

allfviz <- makefvizdf(tissuelevels, alllevels, sexlevels)

@@

gh <- plot_grid(g,h, legend, nrow = 1, rel_widths = c(1, 1, 1), labels = c("h", "i", NULL ), label_size = 12)
gh
plot_grid(def, gh, nrow = 2)

g2 <- fviz_screeplot(allfviz, addlabels = TRUE, ylim = c(0, 50),  ncp = 5, barcolor = "white", barfill = "white") + 
  labs(title = NULL, y = "PC Variance") + theme_B3() 
h2 <- fviz_pca_var(allfviz,  labelsize = 3 , axes.linetype = "blank", 
                   repel = TRUE ,
                  select.var= list(contrib = 5)) + 
      theme_B3() + 
      labs(x = "PC1 (35.8%)", y = "PC2 (32.5%)", title =  NULL) +
      theme( axis.text = element_blank())

legend2 <- png::readPNG("../figures/images/DoveParentsRNAseq_legend.png")
legend2 <-  grid::rasterGrob(legend2, interpolate=TRUE)

gh2 <- plot_grid(g2,h2, legend2, nrow = 1, rel_widths = c(1, 1, 1), labels = c("h", "i", NULL ), label_size = 12)
gh2
plot_grid(def2, gh2, nrow = 2)
```

```{r PCA-tSNE, fig.height= 7, fig.width=7}
plot_grid( abc, def, gh, nrow = 3)
plot_grid( abc2, def2, gh2, nrow = 3)
